\documentclass[10pt, letterpaper]{article}

\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm, footskip=1.0cm]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Tom Beaug\'e's CV},
    pdfauthor={Tom Beaug\'e},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage{paracol}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

\newenvironment{highlights}{
    \begin{itemize}[topsep=0.10cm, parsep=0.10cm, partopsep=0pt, itemsep=0pt, leftmargin=10pt]
}{
    \end{itemize}
}

\begin{document}

\begin{center}
    {\LARGE Tom Beaug\'e} \\[5pt]
    Bertrange, Luxembourg \ | \ Lausanne, Switzerland \\
    \href{mailto:t.beauge@protonmail.com}{t.beauge@protonmail.com} \quad
    +33 7 68 84 76 09 \\
    \href{https://github.com/tombeauge}{github.com/tombeauge} \
    \href{https://www.linkedin.com/in/tombeauge/}{linkedin.com/in/tombeauge}
\end{center}

\section{Education}
\textbf{EPFL - École Polytechnique Fédérale de Lausanne (Switzerland)} \hfill Aug 2024 -- Present \\
\textit{Bachelor in Computer Science} \\[5pt]

\textbf{European School of Luxembourg II, Mamer (Luxembourg)} \hfill Sep 2017 -- Jul 2024 \\
\textit{European Baccalaureate (English Section)} \\ 
Specializations: Advanced Mathematics, Economics, Computer Science, Physics, History \\[3pt]
\textbf{Distinction:} Final Grade 87.67\%, awarded First Prize in Economics

\section{Work Experience}

\textbf{Intern, Cebi S.A.}, Luxembourg \hfill Nov 2022 \\
\begin{highlights}
    \item Deployed heat and humidity sensors across the manufacturing plant to support the company’s transition to Industry 4.0.
    \item Integrated sensor data into the company’s Internet of Things (IoT) infrastructure, enhancing real-time monitoring capabilities.
    \item Applied programming and CAD software skills to optimize sensor placement and data transmission efficiency.
    \item Analyzed collected data to identify trends and insights, and presented technical findings, contributing to process optimization and operational efficiency.
\end{highlights}

\textbf{Intern, Natixis CIB (Trading Desk)}, Paris, France \hfill Jun 2022 -- Jul 2022 \\
\begin{highlights}
    \item Gained exposure to financial markets, specifically bond trading and swap strategies, by working on a desk specializing in swaps for supranational institutions.
    \item Actively engaged with professionals involved in trading bonds, selling Forex derivatives, and syndication activities.
    \item Priced bonds using market data and financial models to support trading decisions and optimize deal execution.
\end{highlights}

\textbf{Municipal Worker, Bertrange Commune}, Luxembourg \hfill Summers 2022, 2023 \\
\begin{highlights}
    \item Maintained public green spaces by removing litter, clearing overgrown areas, and ensuring a clean, safe environment.
    \item Supported logistical operations by assisting in the setup of major town events and festivals.
\end{highlights}

\section{Personal Projects}
\textbf{Option Pricing Models Exploration} \hfill Jan 2025 -- Present \\
\begin{highlights}
    \item Developed and implemented single-period and multi-period binomial tree models for option pricing using Java, focusing on no-arbitrage principles and risk-neutral valuation.
    \item Explored the Black-Scholes model, applying concepts from stochastic calculus and geometric Brownian motion to derive option prices in continuous-time frameworks.
    \item Analyzed model limitations, proposing extensions for American options, volatility structures, and dynamic hedging strategies.
    \item Utilized Python for data visualization, generating performance graphs to analyze computational efficiency.
    \item Authored a comprehensive technical report detailing the theoretical foundations, implementation, and performance analysis of the models.
    \item All code, documentation, and the report are available on my \href{https://github.com/tombeauge}{GitHub repository}.
\end{highlights} 

\textbf{Automated Customer Service Bot} \hfill Jan 2023 \\
\begin{highlights}
    \item Designed and developed an automated customer service bot in Python to manage and respond to emails in real-time.
    \item Integrated OpenAI's API for generating intelligent, context-aware responses based on customer queries.
    \item Utilized SMTP and IMAP protocols to handle email communication, including fetching unread emails and sending automated replies.
\end{highlights}

\section{Skills}
\textbf{Programming Languages:} Java, C, Python, Arduino, basic HTML/CSS/JavaScript, LaTeX \\
\textbf{Languages:} French (Native), English (Bilingual), Spanish (B2)

\section{Activities}

\textbf{Model European Parliament (MEP)}, Luxembourg \hfill Feb 2023 \\
\begin{highlights}
    \item Served as a Portuguese delegate in the Foreign Affairs Committee, advocating for cybersecurity reforms in EU legislation.
\end{highlights}

\textbf{European Schools Sailing Cup}, Croatia \hfill May 2022, 2023 \\
\begin{highlights}
    \item Captained my school’s team in the European Schools Sailing Cup in Croatia for two consecutive years, participating in a week-long regatta.
\end{highlights}

\textbf{Volunteer, Course Contre la Faim}, Luxembourg \hfill May 2021 \\
\begin{highlights}
    \item Organized awareness campaigns and supported event logistics for a fundraising race against hunger.
\end{highlights}

\end{document}
